---
title: "230 Final Project"
author: "Elias Cheruthottil"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

```{r}
df <- read_csv("230 project - Form Responses 1.csv")
```

```{r}
df <- df %>%
  rename(
    Major = `What is your major?`,
    GPA = `What is you GPA?`,
    Credits = `How many credits are you taking a semester`
  ) %>%
  mutate(
    GPA = as.numeric(GPA),
    Credits = parse_number(Credits)
  )
```

```{r}
ggplot(df, aes(x = GPA)) +
  geom_histogram(binwidth = 0.2, fill = "orange", color = "black") +
  geom_density(aes(y = ..count.. * 0.2), color = "blue", size = 1) +
  labs(title = "Histogram of GPA", x = "GPA", y = "Frequency")

```

```{r}
ggplot(df, aes(x = Major, y = GPA)) +
  geom_boxplot(fill = "lightblue") +
  labs(title = "Boxplot of GPA by Major", x = "Major", y = "GPA") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
ggplot(df, aes(x = Credits, y = GPA)) +
  geom_point(color = "darkorange") +
  labs(title = "Scatterplot of GPA vs Credits", x = "Credits", y = "GPA")
```

```{r}
df %>%
  group_by(Major) %>%
  summarise(
    mean_GPA = mean(GPA, na.rm = TRUE),
    sd_GPA = sd(GPA, na.rm = TRUE),
    min_GPA = min(GPA, na.rm = TRUE),
    max_GPA = max(GPA, na.rm = TRUE)
  )
```

#2 Questions

#1. Is there a relationship between the number of credits a student takes and their GPA?

```{r}
cor_test <- cor.test(df$Credits, df$GPA)
lm_model <- lm(GPA ~ Credits, data = df)
summary(lm_model)
```
#The scatterplot of GPA vs  credits shows that there is no strong linear correlation between the number of credits taken and GPA. Students taking both a lower and a high numbers of credits have a wide range of GPAs, showing that the amount of credits alone does not determine academic performance of a student.
    
#2.  Do students in certain majors tend to have higher GPAs than others?

```{r}
anova_model <- aov(GPA ~ Major, data = df)
summary(anova_model)
```
#Yes, the boxplot and summary statistics show differences in GPA across majors. For example, students majoring in Computer Science and Mathematics, and Elementary Education and Humanities showed to have higher median GPAs, while those in IT/MS Cybersecurity and Marine Biology showed having a lower average GPAs. This suggests that major choice may influence a students. GPA






